---
title: "Intensity analysis"
output:
  html_document:
    df_print: paged
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: no
  pdf_document:
    toc: yes
---

# Choose Path and File
```{r}
#################################
##        Variables            ##
##                             ##
##    Path                     ##
##    File                     ##
##                             ##
#################################

Path='C:/Users/m/Desktop/GCaMP_CogRx/'
File="All_Experiments_BaseTreat_DeltaF_Peaks.csv"


```

# Required libraries
```{r}

library(readr)
library(plyr)
library(forcats)
library(lme4)
library(ggplot2)
library(stargazer)
library(lmerTest)
library(rcompanion)
library(dplyr)
library(tidyverse)
library(emmeans)
library(reshape2)
library(tidyr)
library(qwraps2)
library(arsenal)
library(table1)
library(plotrix)
library(ggResidpanel)
library(corrplot)
library(data.table)
library(GGally)
library(ggpubr)

#install.packages("corrplot")
#source("http://www.sthda.com/upload/rquery_cormat.r")

#install.packages("GGally")
#source("https://raw.githubusercontent.com/briatte/ggcorr/master/ggcorr.R")


```

# Set working directory (for .rmd scripts)
```{r setup}

knitr::opts_knit$set(root.dir = Path)

```

# Load File
```{r}

Absolute <- read_csv(file.path(Path,File), col_types = cols (Case = 'f'))


```


# OPTIONAL - Filter by size or intensity
```{r}

# Absolute <- Absolute[!(Absolute$Area<50),]
# Absolute <- Absolute[!(Absolute$max_Intensity<10),]
# 
# 
 Absolute_Treatment <- Absolute[!(Absolute$Treatment=='baseline'),]
# Absolute_Treatment <- Absolute_Treatment[!(Absolute_Treatment$Area<50),]
# Absolute_Treatment <- Absolute_Treatment[!(Absolute_Treatment$max_Intensity<5),]

# #remove inf and nan 
# library(IDPmisc)
# Absolute_Treatment <- NaRV.omit(Absolute_Treatment)

```


# STATS

## Absolute Intensities Baseline and Treated

### 1.Max intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(max_Intensity~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Transform to improve data
Absolute$max_Intensity_ratio_tukey <- transformTukey(Absolute$max_Intensity)
ME_peak_number2<- lmer(max_Intensity_ratio_tukey~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Boxplot
Absolute %>%
  ggplot( aes(x=Abeta, y=max_Intensity, fill=Treatment)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Drug)

# Boxplot
Absolute %>%
  ggplot( aes(x=Drug, y=max_Intensity, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Experiment)



```



### 2.Mean intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(mean_Intensity~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Transform to improve data
Absolute$mean_Intensity_ratio_tukey <- transformTukey(Absolute$mean_Intensity)
ME_peak_number2<- lmer(mean_Intensity_ratio_tukey~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Boxplot
Absolute %>%
  ggplot( aes(x=Abeta, y=mean_Intensity, fill=Treatment)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Drug)

# Boxplot
Absolute %>%
  ggplot( aes(x=Abeta, y=mean_Intensity, fill=Drug)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Treatment)

# # Boxplot
#   ggpaired(Absolute, x='Abeta',y='Min_Intensity', color = "Abeta", line.color = "gray", line.size = 0.4,
#          palette = "jco")+
#   stat_compare_means(label = "p.format")+
#   facet_wrap(~  Drug  ~ Treatment)


```


### 3.Min intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(min_Intensity~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Transform to improve data
Absolute$min_Intensity_ratio_tukey <- transformTukey(Absolute$min_Intensity)
ME_peak_number2<- lmer(min_Intensity_ratio_tukey~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Boxplot
Absolute %>%
  ggplot( aes(x=Abeta, y=min_Intensity, fill=Treatment)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Drug)

# Boxplot
Absolute %>%
  ggplot( aes(x=Drug, y=min_Intensity, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Treatment)

    
```

### 4. Peak number
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(Peak_number~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Transform to improve data
Absolute$Peak_number_ratio_tukey <- transformTukey(Absolute$Peak_number)
ME_peak_number2<- lmer(Peak_number_ratio_tukey~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Boxplot
Absolute %>%
  ggplot( aes(x=Abeta, y=Peak_number, fill=Treatment)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Drug)

# Boxplot
Absolute %>%
  ggplot( aes(x=Drug, y=Peak_number, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Treatment)


    
```

### 5. Peak Frequency
```{r}
                                  
# Linear model + posthoc
ME_peak_frequency2<- lmer(Peak_frequency~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peak_frequency2)
resid_panel(ME_peak_frequency2)
anova(ME_peak_frequency2)
emmeans(ME_peak_frequency2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Transform to improve data
Absolute$Peak_frequency_ratio_tukey <- transformTukey(Absolute$Peak_frequency)
ME_peak_frequency2<- lmer(Peak_frequency_ratio_tukey~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peak_frequency2)
resid_panel(ME_peak_frequency2)
anova(ME_peak_frequency2)
emmeans(ME_peak_frequency2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Boxplot
Absolute %>%
  ggplot( aes(x=Abeta, y=Peak_frequency, fill=Treatment)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Drug)

# Boxplot
Absolute %>%
  ggplot( aes(x=Drug, y=Peak_frequency, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Treatment)

    
```


### 6. Peak Median Width
```{r}
                                  
# Linear model + posthoc
ME_peaks_median_width2<- lmer(peaks_median_width~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peaks_median_width2)
resid_panel(ME_peaks_median_width2)
anova(ME_peaks_median_width2)
emmeans(ME_peaks_median_width2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Transform to improve data
Absolute$peaks_median_width_ratio_tukey <- transformTukey(Absolute$peaks_median_width)
ME_peaks_median_width2<- lmer(peaks_median_width_ratio_tukey~Abeta*Drug*Treatment+(1|Case)+(1|Experiment),data = Absolute)
summary(ME_peaks_median_width2)
resid_panel(ME_peaks_median_width2)
anova(ME_peaks_median_width2)
emmeans(ME_peaks_median_width2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Boxplot
Absolute %>%
  ggplot( aes(x=Abeta, y=peaks_median_width, fill=Treatment)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Drug)

# Boxplot
Absolute %>%
  ggplot( aes(x=Drug, y=peaks_median_width, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Treatment)

    
```




## Absolute Intensities Treatment only

### 1.Max intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(max_Intensity~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Transform to improve data
Absolute_Treatment$max_Intensity_ratio_tukey <- transformTukey(Absolute_Treatment$max_Intensity)
ME_peak_number2<- lmer(max_Intensity_ratio_tukey~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Abeta, y=max_Intensity, fill=Drug)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Drug, y=max_Intensity, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)



```



### 2.Mean intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(mean_Intensity~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Transform to improve data
Absolute_Treatment$mean_Intensity_ratio_tukey <- transformTukey(Absolute_Treatment$mean_Intensity)
ME_peak_number2<- lmer(mean_Intensity_ratio_tukey~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Abeta, y=mean_Intensity, fill=Drug)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Drug, y=mean_Intensity, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)



```


### 3.Min intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(min_Intensity~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Transform to improve data
Absolute_Treatment$min_Intensity_ratio_tukey <- transformTukey(Absolute_Treatment$min_Intensity)
ME_peak_number2<- lmer(min_Intensity_ratio_tukey~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Abeta, y=min_Intensity, fill=Drug)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Drug, y=min_Intensity, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

    
```

    
### 4. Peak number
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(Peak_number~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Transform to improve data
Absolute_Treatment$Peak_number_ratio_tukey <- transformTukey(Absolute_Treatment$Peak_number)
ME_peak_number2<- lmer(Peak_number_ratio_tukey~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Abeta, y=Peak_number, fill=Drug)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)


# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Drug, y=Peak_number, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)


    
```

### 5. Peak Frequency
```{r}
                                  
# Linear model + posthoc
ME_peak_frequency2<- lmer(Peak_frequency~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peak_frequency2)
resid_panel(ME_peak_frequency2)
anova(ME_peak_frequency2)
emmeans(ME_peak_frequency2, pairwise ~ Abeta*Drug, adjust="tukey")

# Transform to improve data
Absolute_Treatment$Peak_frequency_ratio_tukey <- transformTukey(Absolute_Treatment$Peak_frequency)
ME_peak_frequency2<- lmer(Peak_frequency_ratio_tukey~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peak_frequency2)
resid_panel(ME_peak_frequency2)
anova(ME_peak_frequency2)
emmeans(ME_peak_frequency2, pairwise ~ Abeta*Drug, adjust="tukey")

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Abeta, y=Peak_frequency, fill=Drug)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Drug, y=Peak_frequency, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

    
```


### 6. Peak Median Width
```{r}
                                  
# Linear model + posthoc
ME_peaks_median_width2<- lmer(peaks_median_width~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peaks_median_width2)
resid_panel(ME_peaks_median_width2)
anova(ME_peaks_median_width2)
emmeans(ME_peaks_median_width2, pairwise ~ Abeta*Drug, adjust="tukey")

# Transform to improve data
Absolute_Treatment$peaks_median_width_ratio_tukey <- transformTukey(Absolute_Treatment$peaks_median_width)
ME_peaks_median_width2<- lmer(peaks_median_width_ratio_tukey~Abeta*Drug+(1|Case)+(1|Experiment),data = Absolute_Treatment)
summary(ME_peaks_median_width2)
resid_panel(ME_peaks_median_width2)
anova(ME_peaks_median_width2)
emmeans(ME_peaks_median_width2, pairwise ~ Abeta*Drug, adjust="tukey")

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Abeta, y=peaks_median_width, fill=Drug)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

# Boxplot
Absolute_Treatment %>%
  ggplot( aes(x=Drug, y=peaks_median_width, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

    
```
