---
title: "Intensity analysis"
output:
  html_document:
    df_print: paged
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: no
  pdf_document:
    toc: yes
---

# Choose Path and File
```{r}
#################################
##        Variables            ##
##                             ##
##    Path                     ##
##    File                     ##
##                             ##
#################################

Path='C:/Users/m/Desktop/GCaMP_CogRx/2021.12.07_GCaMP6/7_Analysis/'

File="Intensities_Smooth_BleachCorr_Conditions.csv"

```

# Required libraries
```{r}

library(readr)
library(plyr)
library(forcats)
library(lme4)
library(ggplot2)
library(stargazer)
library(lmerTest)
library(rcompanion)
library(dplyr)
library(tidyverse)
library(emmeans)
library(reshape2)
library(tidyr)
library(qwraps2)
library(arsenal)
library(table1)
library(plotrix)
library(ggResidpanel)
library(corrplot)
library(data.table)

#install.packages("corrplot")
#source("http://www.sthda.com/upload/rquery_cormat.r")

#install.packages("GGally")
#source("https://raw.githubusercontent.com/briatte/ggcorr/master/ggcorr.R")


```

# Set working directory (for .rmd scripts)
```{r setup}

knitr::opts_knit$set(root.dir = Path)

```

# Load File
```{r}

DATA <- read_csv(File, col_types = cols (Case = 'f'))

```



## Summarize by object and create ratios
```{r}

 
Cases_list<-levels(DATA$Case)

for (j in 1: length (Cases_list)){

 working_case<-subset(DATA, Case==Cases_list[j])
 
 working_case$Case_treatment=as.character(working_case$Case) #will be changed to group them later
 
 # Create a summary by cells and by Treatment
  Summary_by_Treatment <-working_case %>%
  group_by (Object, Treatment) %>%
  
  summarise (Case=Case[1],Abeta=Abeta[1], Drug=Drug[1], Object=Object[1],Mean_Intensity=mean(Intensity),  Max_Intensity=max(Intensity),Min_Intensity=min(Intensity), Mean_Area=mean(Area)) 


 # Create a summary by cells for ratios
  Summary_by_Cell <-working_case %>%
 group_by (Object) %>%
  
  summarise (Case=Case[1],Abeta=Abeta[1], Drug=Drug[1], Object=Object[1], Mean_Area=mean(Area)) 

  Added_Columns <- c('Mean_Intensity_ratio', 'Max_Intensity_ratio', 'Min_Intensity_ratio')
Summary_by_Cell[ , Added_Columns] <- NA


for (i in 1:max (Summary_by_Treatment$Object)) {
  
  working_cell <- subset (Summary_by_Treatment, Object==i)
  

  Summary_by_Cell$Mean_Intensity_ratio[i] <- (working_cell$Mean_Intensity[working_cell$Treatment=='treatment'] / working_cell$Mean_Intensity[working_cell$Treatment=='baseline'])
  
  Summary_by_Cell$Max_Intensity_ratio[i] <- (working_cell$Max_Intensity[working_cell$Treatment=='treatment'] / working_cell$Max_Intensity[working_cell$Treatment=='baseline'])
  
  Summary_by_Cell$Min_Intensity_ratio[i] <- (working_cell$Min_Intensity[working_cell$Treatment=='treatment'] / working_cell$Min_Intensity[working_cell$Treatment=='baseline'])
  
 
}


  if (j==1){
    All_Cases_summary<- Summary_by_Treatment
  }  else {
    All_Cases_summary<- rbind (All_Cases_summary, Summary_by_Treatment)
  }


  if (j==1){
    All_Cases_ratio<- Summary_by_Cell
  }  else {
    All_Cases_ratio<- rbind (All_Cases_ratio, Summary_by_Cell)
  }

}

#remove inf and nan 
library(IDPmisc)
All_Cases_summary <- NaRV.omit(All_Cases_summary)
All_Cases_ratio <- NaRV.omit(All_Cases_ratio)

# Create another summary to compare only absolute intensities of Baseline and Treatment
All_Cases_BaseTreat <- All_Cases_summary[!(All_Cases_summary$Treatment=='ionomycine'| All_Cases_summary$Treatment=='EGTA'),]

```

# STATS

## Absolute Intensities All Contitions (removed to simplify, by now not included Ionomycine and EGTA)


## Absolute Intensities Baseline and Treated
### 1.Max intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(Max_Intensity~Abeta*Drug*Treatment+(1|Case),data = All_Cases_BaseTreat)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Transform to improve data
# All_Cases_BaseTreat$Max_Intensity_ratio_tukey <- transformTukey(All_Cases_BaseTreat$Max_Intensity)
# ME_peak_number2<- lmer(Max_Intensity_ratio_tukey~Abeta*Drug*Treatment+(1|Case),data = All_Cases_BaseTreat)
# summary(ME_peak_number2)
# resid_panel(ME_peak_number2)
# anova(ME_peak_number2)
# emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Boxplot
All_Cases_BaseTreat %>%
  ggplot( aes(x=Abeta, y=Max_Intensity, fill=Treatment)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Drug)

# Boxplot
All_Cases_BaseTreat %>%
  ggplot( aes(x=Drug, y=Max_Intensity, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Treatment)

    
```

### 2.Mean intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(Mean_Intensity~Abeta*Drug*Treatment+(1|Case),data = All_Cases_BaseTreat)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Transform to improve data
# All_Cases_BaseTreat$Mean_Intensity_ratio_tukey <- transformTukey(All_Cases_BaseTreat$Mean_Intensity)
# ME_peak_number2<- lmer(Mean_Intensity_ratio_tukey~Abeta*Drug*Treatment+(1|Case),data = All_Cases_BaseTreat)
# summary(ME_peak_number2)
# resid_panel(ME_peak_number2)
# anova(ME_peak_number2)
# emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Boxplot
All_Cases_BaseTreat %>%
  ggplot( aes(x=Abeta, y=Mean_Intensity, fill=Treatment)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Drug)

# Boxplot
All_Cases_BaseTreat %>%
  ggplot( aes(x=Drug, y=Mean_Intensity, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Treatment)

    
```

### 3.Min intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(Min_Intensity~Abeta*Drug*Treatment+(1|Case),data = All_Cases_BaseTreat)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Transform to improve data
# All_Cases_BaseTreat$Min_Intensity_ratio_tukey <- transformTukey(All_Cases_BaseTreat$Min_Intensity)
# ME_peak_number2<- lmer(Min_Intensity_ratio_tukey~Abeta*Drug*Treatment+(1|Case),data = All_Cases_BaseTreat)
# summary(ME_peak_number2)
# resid_panel(ME_peak_number2)
# anova(ME_peak_number2)
# emmeans(ME_peak_number2, pairwise ~ Abeta*Drug*Treatment, adjust="tukey")

# Boxplot
All_Cases_BaseTreat %>%
  ggplot( aes(x=Abeta, y=Min_Intensity, fill=Treatment)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Drug)

# Boxplot
All_Cases_BaseTreat %>%
  ggplot( aes(x=Drug, y=Min_Intensity, fill=Abeta)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)+
  facet_wrap(~  Treatment)

    
```




## Ratio Treatment/Baseline
### 1.Max intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(Max_Intensity_ratio~Abeta*Drug+(1|Case),data = All_Cases_ratio)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
#emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Transform to improve data
# All_Cases_summary$Max_Intensity_ratio_tukey <- transformTukey(All_Cases_ratio$Max_Intensity_ratio)
# ME_peak_number2<- lmer(Max_Intensity_ratio_tukey~Abeta*Drug+(1|Case),data = All_Cases_ratio)
# summary(ME_peak_number2)
# resid_panel(ME_peak_number2)
# anova(ME_peak_number2)
# #emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Boxplot
All_Cases_ratio %>%
  ggplot( aes(x=Abeta, y=Max_Intensity_ratio, fill=Drug)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

    
```

### 2.Min intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(Min_Intensity_ratio~Abeta*Drug+(1|Case),data = All_Cases_ratio)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Transform to improve data
# All_Cases_summary$Max_Intensity_ratio_tukey <- transformTukey(All_Cases_ratio$Max_Intensity_ratio)
# ME_peak_number2<- lmer(Max_Intensity_ratio_tukey~Abeta*Drug+(1|Case),data = All_Cases_ratio)
# summary(ME_peak_number2)
# resid_panel(ME_peak_number2)
# anova(ME_peak_number2)
# #emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Boxplot
All_Cases_ratio %>%
  ggplot( aes(x=Abeta, y=Min_Intensity_ratio, fill=Drug)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

    
```

### 3.Mean intensity
```{r}
                                  
# Linear model + posthoc
ME_peak_number2<- lmer(Mean_Intensity_ratio~Abeta*Drug+(1|Case),data = All_Cases_ratio)
summary(ME_peak_number2)
resid_panel(ME_peak_number2)
anova(ME_peak_number2)
emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Transform to improve data
# All_Cases_summary$Max_Intensity_ratio_tukey <- transformTukey(All_Cases_ratio$Max_Intensity_ratio)
# ME_peak_number2<- lmer(Max_Intensity_ratio_tukey~Abeta*Drug+(1|Case),data = All_Cases_ratio)
# summary(ME_peak_number2)
# resid_panel(ME_peak_number2)
# anova(ME_peak_number2)
# #emmeans(ME_peak_number2, pairwise ~ Abeta*Drug, adjust="tukey")

# Boxplot
All_Cases_ratio %>%
  ggplot( aes(x=Abeta, y=Mean_Intensity_ratio, fill=Drug)) +
  geom_boxplot() +
  geom_boxplot(outlier.size = -1, width=0.75)

```





```{r}

 # Save table
 # Can be changed to csv2 instead of csv
 directory=getwd()
 Filename=file.path(directory,paste(tools::file_path_sans_ext(File),'_Summary_BaseTreat.csv', sep=''))
 write.csv (All_Cases_BaseTreat, Filename, row.names = FALSE)
 
 Filename2=file.path(directory,paste(tools::file_path_sans_ext(File),'_Summary_ratio.csv', sep=''))
 write.csv (All_Cases_ratio, Filename2, row.names = FALSE)
  
```

    

